The LBRY Trending Algorithm

### 2021-11-18 tex/ms.tex
Sentence fixup

To compute updated trending scores, we need to add and multiply
values using Equations~\ref{eqn:sparse_update}~and~\ref{eqn:spike_mass}, but on the
squashed grade. In other words, if we have squashed values $x$ and
$y$, we will need the squashed sum
\begin{align}
x \oplus y &= S(U(x) + U(y))
\end{align}
and the squashed product
\begin{align}
x \otimes y &= S(U(x)U(y)).
\end{align}
These can be worked out in terms of logsumexp and logdiffexp.
The results are fairly complicated and are given in the Appendix.

>>>>

To compute updated trending scores, we need to add and multiply
values using Equations~\ref{eqn:sparse_update}~and~\ref{eqn:spike_mass}, but on the
squashed grade. In other words, if we have squashed values $x$ and
$y$, we will need the squashed sum
\begin{align}
x \oplus y &= S(U(x) + U(y))
\end{align}
and the squashed product
\begin{align}
x \otimes y &= S(U(x)U(y)).
\end{align}
These can be worked out in terms of logsumexp and logdiffexp, and thus can
be computed relatively easily without overflow.
The results are given in the Appendix.
